
---
title: Pre-analysis plan and design description
author: Jake Bowers
date: '`r format(Sys.Date(), "%B %d, %Y")`'
fontsize: 11pt
geometry: margin=1in
graphics: yes
indent: false
bibliography:
 - ../refs.bib
biblio-style: authoryear-comp
output:
  pdf_document:
    toc: true
    number_sections: true
    fig_caption: yes
    fig_height: 4
    fig_width: 4
    latex_engine: xelatex
    keep_tex: true
    citation_package: biblatex
    md_extensions: +raw_attribute
---

```{r echo=FALSE, include=FALSE, cache=FALSE}
library(here)
source(here::here("Analysis","rmarkdownsetup.R"))
```

```{r setup1, echo=FALSE}
library(RItools)
library(optmatch)
library(tidyverse)
library(arm)
library(tidyverse)
library(formula.tools)
library(coin)
load(here::here("Analysis","match_data_prep.rda"),verbose=TRUE)
load(here::here("Analysis","initial_balance.rda"),verbose=TRUE)
##  First, drop the observations for the placebo pharmacies

table(wdat17i$soldvsnot17,exclude=c())
table(wdat17p$soldvsnot17,exclude=c())

dat17i <- wdat17i %>% filter(!is.na(soldvsnot17))
table(dat17i$soldvsnot17,exclude=c())

dat17p <- wdat17p %>% filter(!is.na(soldvsnot17))
table(dat17p$soldvsnot17,exclude=c())

load(here::here("Analysis","design_soldvsnot.rda"),verbose=TRUE)
```

We aim to assess the effect of living near a pharmacy that sells marijuana on
the attitudes and perceptions of the neighbors after living near that selling
pharmacy for one year.

# Study Design Overview

## Data Collection: Pharmacies and Neighbors Survey

The data used in this analysis come from face-to-face surveys that aimed to help
us measure the crime victimization experienced by those living near pharmacies
and their attitudes towards the law and public insecurity. None of these surveys
were intended to be representative of the Uruguayan population. We conducted two
rounds of surveys with neighbors of selling and non selling pharmacies. In the
first survey round, fieldwork started on June 17, 2017 and finished in July 1,
2017 before the sales started (July 19, 2017). The sample contains 600 neighbors
of 60 pharmacies, 10 neighbors per pharmacy. The list of pharmacies joining the
dispensation was confidential until the sale started, so this initial group of
neighbors did not know if their closest pharmacy was going to sell.

The second round of the survey was carried out approximately one year later, between August 9 and September 30, 2018. Overall, we have conducted 1298 interviews across the country in the two rounds. Respondents were selected among people over 18 years old that lived in the sampled household and were present at the moment of the interview. The most recent birthday selection process was used to choose among households residents.

\subsection{Selling and Non-selling Pharmacies}
In addition to neighbors, we also interviewed one representative of each pharmacy (sellers and non-sellers) in both rounds. Overall, we conducted 119 surveys with representatives (59 in 2017 and 60 en 2018). Because marijuana selling was not randomly assigned by the government to pharmacies, and each pharmacy decided to adhere or not to the selling, those that sell and those that do not sell might be different. Data from the pharmacies' representatives survey allowed us to characterize selling and non-selling pharmacies, and analyze if there were any initial differences between them that could explain the differences on outcomes.

Selling and non-selling pharmacies are not different in terms of their general characteristics. The only relevant distinction is that among non-selling there are stores that are part of a pharmacy's chain. In terms of infrastructure both selling and non-selling pharmacies are quite similar, and they are also similar regarding security measures, insecurity perceptions and crime victimization. The later goes against the idea that pharmacies that sell cannabis did so because they are better equipped in terms of security protection, have suffered less crimes and feel more secure in their neighborhoods. There are not significant differences either in their perceptions about cannabis and its users.

The most important distinction among sellers and non-sellers is concerning opinions towards the public policy. Owners and representatives of pharmacies that decided to sell are consistently more in favor of the regulation and anticipate it would have more positive impacts. Balance tests (see Table \ref{tab:pharmaciesperceptions} in Appendix A) show statistically significant differences between sellers and non-sellers among almost all outcomes related with policy opinions. The only exception is the perceived impact on drug trafficking in which there are no significant differences. In addition sellers are significantly more against the idea that cannabis is a gateway drug than non sellers.

## Changes in Selling Pharmacies

Our initial sample contained 42 non-selling pharmacies and 18 selling ones. Figure \ref{fig:ctrltrtpharms_1} shows the geographical distribution of the pharmacies in our study. During the first year of policy implementation, some changes in the pharmacies selling group occurred. First, two pharmacies that initially were registered to sell, never actually did it: this reduced our selling group to 16. Second, six pharmacies that had entered the system abandoned it due to the prohibition imposed by US banks that forbid cannabis selling pharmacies to operate with bank accounts.\footnote{For information about the problem with the banking system see: \url{https://www.elobservador.com.uy/nota/brou-cierra-cuentas-vinculadas-con-marihuana-y-mas-farmacias-evaluan-dejar-de-venderla-20178175004}.} And third, because pharmacy registration remained open, 4 new pharmacies entered the system.

This means that by the second round of data collection we had (1) pharmacies that never sold and never registered to do it (n=42) that we call ``control'' or ``comparison'' pharmacies, (2) two pharmacies that never sold but initially were willing to do it (n=2) named as ``placebo'' pharmacies, (3)  pharmacies that sold cannabis during the entire time between the first and second round (n=10) that we label as ``wholetime'', (4) pharmacies that dropped out from 2017 to 2018 (n=6) that we call ``dropouts'', and (5) pharmacies that joined the system at some point between the 2017 round and 2018 round (n=4) that we call ``newcomers'' (see Table \ref{tab:pharmsalestatus}).

\begin{figure}[htpb!]
    \centering
    \label{fig:ctrltrtpharms_1}
    \caption{Pharmacies registered to sell marijuana and comparison pharmacies}
    \includegraphics[width=6.5in,height=3.4851in]{../media/country.png}
\footnotesize{Note: green symbols show pharmacies registered to sell marijuana as of June 2017. \\ Blue symbols are comparison pharmacies.}
\end{figure}

The comparison group was selected following four criteria that aimed to produce a set of pharmacies that was not selling cannabis where the neighborhood characteristics would be at least roughly similar to the neighborhood characteristics of the selling pharmacies. We further enhance these comparisons using matching to create strata as described below. Here we describe the first steps in our selection process. The first criteria was ``same  geographical unit'':  pharmacies in the same administrative region (the ``departamento'') without at least one selling pharmacy were deleted from the sampling frame. The second criteria was ``population density'':  pharmacies in rural areas were deleted from the sample because none of the selling pharmacies is located in rural areas. The third criteria was``criminality rate'': pharmacies in neighborhoods (for Montevideo) or cities where homicides reports, assaults reports and robberies reports are too high or too low  in comparison with the neighborhoods where selling pharmacies were situated, were discarded. The fourth criteria is ``distance'': pharmacies in the control group should be at least 6 blocks away from any treatment pharmacy. After eliminating the pharmacies that did not pass the four criteria, we randomly selected 42 control pharmacies among the about 1000 pharmacies that exist in the country \footnote{We used official sociodemographic information about the neighbourhoods/localities/``departamentos''. See Table \ref{tab:phlongtable} in Appendix A for more details on the pharmacies characteristics}.

\begin{small}
\begin{table}[htbp!]
\scriptsize
  \centering
   \caption{Status of  marijuana selling pharmacies}
  \label{tab:pharmsalestatus}
  \begin{tabular}{@{}lllcccccc@{}}
\textbf{Pharmacy}  &  \textbf{Neighborhood}  &  \textbf{Dpt.}  &  \textbf{Round 1}  &  \textbf{Round 2}  &  \textbf{Entrance}  &  \textbf{Drop out}  &  \textbf{Type}  \\
\midrule
Antartida     &     Centro     &     Montevideo     &     Yes     &     Yes     &     7/19/17     &        &     wholetime  \\
 Caceres      &     Pocitos     &     Montevideo     &     Yes     &     Yes     &     7/19/17     &        &     wholetime  \\
 Tapie     &     Ciudad vieja     &     Montevideo     &     Yes     &     Yes     &     7/19/17     &      &     wholetime  \\
 Las toscas     &     Las toscas     &     Canelones     &     Yes     &     Yes     &     7/19/17     &      &     wholetime  \\
 Nueva Brun     &     Trinidad     &     Flores     &     Yes     &     Yes     &     7/19/17     &        &     wholetime  \\
 Gortari     &     Centro     &     Lavalleja     &     Yes     &     Yes     &     7/19/17     &        &     wholetime  \\
 La Cabina     &     Las Flores     &     Maldonado     &     Yes     &     Yes     &     7/19/17     &      &     wholetime  \\
 Termal guaviyu     &     Termas     &     Paysandú     &     Yes     &     Yes     &     7/19/17     &      &     wholetime  \\
 Albisu Termal     &     Pasaje Comercial    &   Salto  &     Yes     &     Yes     &     7/19/17     &     &     wholetime  \\
 Bengoechea     &     Centro     &     Tacurembó     &     Yes     &     Yes     &     7/19/17     &        &     wholetime  \\
 Miguel     &     Canelones centro   &    Canelones   &   Yes     &   Yes     &   7/19/17     &  10/2/17     &     dropouts  \\
 Carmelo     &     Carmelo     &     Colonia     &     Yes     &     Yes     &     7/19/17     &   8/25/17     &     dropouts  \\
 Pitagoras     &     Malvin norte     &     Montevideo     &     Yes     &     Yes     &    7/19/17     &     8/9/17     &     dropouts  \\
 Saga     &     Centro     &     Artigas     &     Yes     &     Yes     &     7/19/17     &   9/6/17     &     dropouts  \\
 Medicci     &     Paysandú     &     Paysandú     &     Yes     &     Yes     &   7/19/17     &     9/1/17     &     dropouts  \\
 Bidegain     &     Libertad     &     San José     &     Yes     &     Yes     &    7/19/17     &     9/1/17     &     dropouts  \\
 Camaño     &     Pocitos     &     Montevideo     &     No     &     Yes     &    9/11/17     &          &     newcomers  \\
 Silleda     &     Brazo oriental     &     Montevideo     &     No     &     Yes     &     9/11/17     &          &     newcomers\\
 Constitución Sur     &     Flor de Maroñas     &     Montevideo     &     No     &     Yes     &     20/4/18     &          &     newcomers  \\
 Lilen     &     Punta Carretas     &     Montevideo     &     No     &     Yes     &     17/5/18     &          &     newcomers  \\
\bottomrule
\end{tabular}
\end{table}
\end{small}


## The Stratification Design


To learn about whether sale of cannabis in pharmacies influences crime
victimization, attitudes and perceptions of neighbors, we compare the survey
responses of neighbors living near pharmacies selling cannabis to the responses
of neighbors who did not live near such pharmacies. The problem arising from a
strategy like this, is that neighborhoods where pharmacy owners decided to sell
cannabis are probably different from neighborhoods where they decided to pass
over the opportunity to sell cannabis (we already know that owners and
representatives of the pharmacies differ on their opinions towards the policy).
The question is whether the amount of difference between the two groups of
pharmacies would mislead our comparison to learn about the effects of selling
cannabis on crime victimization and attitudes. What is the standard to judge
whether a comparison might mislead us? We know that if an intervention is
randomly assigned, then the comparisons based on that intervention would not
confuse causal effects with confounding. \citet{hansen2008cbs} develop a formal
way to compare a given observed comparison with what would be expected if that
comparison had been randomized: in essence, they develop a hypothesis test for
the hypothesis that the neighbors of selling pharmacies and the neighbors of not
selling pharmacies might have been allocated at random. In our case, the raw
comparison of attitudes around pharmacies selling cannabis and those not selling
cannabis, confirms our hunch that the places do not in fact compare favorably to
a randomized experiment:  the Hansen and Bowers omnibus test across 81
covariates reports a $p$-value of `r xb0i$overall[,"p.value"]`.


```{r}
## Another way to see the same result
initial_neigh_bal_fmla <- ~soldvsnot17
tmpfmla <- formula(terms(parms1_res$maxTp@statistic@y))
lhs(initial_neigh_bal_fmla) <- rhs(tmpfmla)
initial_omnibus_bal <-
    independence_test(initial_neigh_bal_fmla,data=dat17p,teststat="quadratic")
```

## Designing a Better Baseline Comparison

If we had managed to convince the government to issue the registrations by
lottery and if a large pool of pharmacies had entered the lottery, we would be
able to say that the pharmacies and nearby neighborhoods selected by lottery to
sell cannabis would be no different from the pharmacies and associated
neighborhoods losing the lottery. This would also be the case if the lottery
occurred in groups of places --- say, the right to sell were randomly assigned
among pharmacies in Montevideo and also among pharmacies outside of Montevideo.
This kind of design would yield a block-randomized experiment. If
Montevideo/Interior were the only observed covariates that might confound our
comparison, we could directly compare pharmacies to each other within area, and
we could compare that stratified design to a hypothetical block-randomized
experiment in order to assess the comparison (just as we did above when we
compared the simple selling-vs-not selling comparison to a simple randomized
experiment with 16 treated and 42 control groups and 81 background covariates).
This is what we do below. We use an optimization strategy to produce a series of
strata that collectively, across 81 observed covariates, compares favorably to a
hypothetical block-randomized experiment. Of course, we do not claim that a
stratified design substitutes for an experiment --- we can only speak to
differences on 81 covariates, not on all possible observed and unobserved as we
could if we had an actually randomized experiment. Later, in
\S~\ref{sec:sensitivity}, we assess the extent to which we might change our
substantive conclusions based on the stratified design due to the influence of
unobserved covariates.\footnote{See \citep[Chapter 3]{rosenbaum2010design} for
an overview of this method of sensitivity analysis.}

Our specific design first creates strata with similar neighborhoods where one
neighborhood has a pharmarcy selling marijuana and the other comparison
neighborhoods were places where a pharmacy did not sell marijuana. This design
compared favorably with a randomized experiment. The algorithm ended up dropping
13 neighborhoods as too different from the focal neighborhoods. 

See the details below:

```{r}
summary(parms1_res$fm_p,max.controls=Inf)
pvalue(parms1_res$maxTp)
```

To further return differences in exposure to a selling pharmacy, we next matched
people to each other within the sets just described. We ended up dropping one
person from one of the comparison neighborhoods, and produced a design that was
mostly pairs with a few people in treated neighborhoods matched to many people
in control neighborhoods.

```{r}
summary(parms1_res$fm_i,max.controls=Inf)
parms1_res$crime_p


```

# Analysis Plan

## Outcomes

We also have a social disorder index: `social_dis` made from  "dis4_i" "dis5_i" "dis6_i" Higher values of the index indicates higher disorder.

Finally, we have created the "activities_index" that show how much people are involved in their neighborhood´s daily life.  This index has a 0-1 scale, 1 meaning greater frequency of activities in the neighborhood and 0 meaning none.  "neigh2_i" "neigh3_i" "neigh4_i" "neigh5_i" "neigh6_i" "neigh7_i" "neigh8_i".

Our outcome variables are the following:

```r
outcomes <- c("n_sec_i","c_sec_i","vic12","dt_impact_i","ps_impact_i","boca1_i","social_dis","activities_index")
```


# Hypotheses

Our  two main confirmatory hypotheses are:
  -   H1: *The sale of marijuana at pharmacies will not have significant
      effects on crime victimization of pharmacies' neighbors*
  
  -   H2: *The sale of marijuana at pharmacies will not have significant
      effects on neighbors' insecurity perceptions*
 
 In adittion we have five exploratory hypotheses:
 
  -   H3: *The sale of marijuana at pharmacies will push "bocas" outside the
      neighborhood, and by doing that, neighbors' insecurity perception
      might be reduced*
  
  -   H4: *The sale of marijuana at pharmacies will increase social disorder
      in the neighborhood, that would lead to higher levels of public
      insecurity perception among neighbors*
  
  -   H5: *The sale of marijuana at pharmacies will diminish citizens'
      insertion in the neighborhood*
  
  -   H6: *The sale of marijuana at pharmacies will not change citizens'
      evaluations about the impact of marijuana legalization on public
      security*
  
  -   H7: *The sale of marijuana at pharmacies will change citizens'
      evaluations about the impact of marijuana legalization on drug
      trafficking*

# Measures and Index Construction

Include the description of all measures, either with the table or text. 

The social disorder index was built using three variables: presence of young people loitering, presence of drunk or stoned people in the streets, and presence of people arguing with each other. Each of these variables have the following values: 1 (Not at all), 2 (Little), 3 (Somewhat), and 4 (Very much). In order to construct the index we assume intermediate substitutability among variables and assign the mean value \citep{goertz2006social}.

Citizens' Insertion on their Neighborhood is an index constructed with eight variables grouped in four dimensions. The dimensions are: use of services (education and health) in the neighborhood, contact among neighbors (chat and/or meet for collective action activities), perform recreational activities in the neighborhood, and shopping in the neighborhood. We assume intermediate substitutability among dimensions and assign the mean value. The use of services dimension has two indicators: use of educational services (kindergarten, school,high school) in the neighborhood and use of health services (doctor, hospital) in the neighborhood. We assume total substitutability among the two indicators and assign the maximum value  \citep{goertz2006social}.Contact among neighbors dimension also has two indicators: talk with your neighbors and meets/ organizes with the neighbors for any improvement activity for the neighborhood. We also assume total substitutability among the two indicators and assign the maximum value. Perform recreational activities in the neighborhood is measured by the question: do you perform any recreational activities in the neighborhood? Finally, shopping in the neighborhood is measured by the question: do you purchase in warehouses or stores in the neighborhood?

We document our index construction in the github repository in `datasetup.do` (date stamped using the commit and date mentioned above).

Table 1. Outcomes variables description

Variable	|	Question	|	Scale	|	Minimum	|	Maximun|
--------	|	--------	|	-----	|	:--------:|	:-------:|
Country insecurity perception | In general, in your country, do you feel very safe somewhat unsafe or very unsafe? |1. Very safe; 2.Somewhat safe; 3. Somewhat unsafe; 4. Very unsafe; 88 - Don\'t know; 99 - No answer |	1	|	4
Neighborhood insecurity perception | And in the neighborhood where you live, do you feel very safe, somewhat safe, somewhat unsafe or very unsafe? |1. Very safe; 2.Somewhat safe; 3. Somewhat unsafe; 4. Very unsafe; 88 - Don\'t know; 99 - No answer |	1	|	4
Crime victimization in the last 12 months | Now, changing the subject, have you been a victim of any type of crime in the past 12 months? That is, have you been a victim of robbery, burglary, assault, fraud, blackmail, extortion, violent threats or any other type of crime in the past 12 months? | 1. Yes; 2. No; 88 - Don\'t know | 1	|	2
Perceived impact on public security |	Now regarding to public safety, because of this law, do you think the country will be better, will remain the same or will be worst?	|	1. Yes;	2. No; 88 - Don\'t know;	99 - No answer| 1	|	3
Perceived impact on drug-trafficking | And regarging the fight against drug-trafficking, do you think the country will be better, will remain the same or will be worst? |	1. Yes;	2. No; 88 - Don\'t know;	99 - No answer| 1	|	2
Reported existence of bocas	|	Based on what you know or hear, there is a any boca in this area? | 1. Yes;	2. No; 88 - Don\'t know;	99 - No answer| 1	|	2
Social Disorder Index	|	Index | 1. Nothing; 2. A little; 3. Something; 4. A lot | 4 | 1
Presence of young people loitering | Observation | 1. Nothing; 2. A little; 3. Something; 4. A lot | 4 | 1
Presence of drunk or stoned people in the streets | Observation | 1. Nothing; 2. A little; 3. Something; 4. A lot | 4 | 1
Presence of people arguing with each other | Observation | 1. Nothing; 2. A little; 3. Something; 4. A lot | 1 | 4
Citizens insertion in the neighborhood | Index | - | 0 | 1
Talk with your neighbors| Finally, thinking about the activities you do in this neighborhood, please tell me how many times you: talk with your neighbors |1. Once a week; 2. Once or twice a week; 3. Once or twice a year; 4. Never; 88. Don\'t know; 99. No answer; |4 | 1
Chat and/or meet for collective action activities | Finally, thinking about the activities you do in this neighborhood, please tell me how many times you: chat and/or meet for collective action activities|1. Once a week; 2. Once or twice a week; 3. Once or twice a year; 4. Never; 88. Don\'t know; 99. No answer; | 4 | 1
Use educational services (kindergarten, school, high school) | Finally, thinking about the activities you do in this neighborhood, please tell me how many times you: use educational services (kindergarten, school, high school)|1. Once a week; 2. Once or twice a week; 3. Once or twice a year; 4. Never; 88. Don\'t know; 99. No answer; | 4 | 1
Use health services (doctor, hospital) | Finally, thinking about the activities you do in this neighborhood, please tell me how many times you: use health services (doctor, hospital) |1. Once a week; 2. Once or twice a week; 3. Once or twice a year; 4. Never; 88. Don\'t know; 99. No answer; | 4 | 1
Buy in local stores | Finally, thinking about the activities you do in this neighborhood, please tell me how many times you: buy in local stores|1. Once a week; 2. Once or twice a week; 3. Once or twice a year; 4. Never; 88. Don\'t know; 99. No answer; | 4 | 1
Perform recreational activities | Finally, thinking about the activities you do in this neighborhood, please tell me how many times you: perform recreational activities|1. Once a week; 2. Once or twice a week; 3. Once or twice a year; 4. Never; 88. Don\'t know; 99. No answer; | 4 | 1


# Estimation Procedure and Inference Criteria

We will report both unadjusted and covariance adjusted results --- focusing on appropriately weighted differences of means as estimators for the average treatment effect. We will analyze the study as-if-randomized --- using Neyman's standard errors and Fisher's hypothesis testing approaches.


## Approaches to estimation

Our covariance adjustment will follow Lin's method (Lin 2013). And we will estimate the ATE (i.e. using block-size weights) but report confidence intervals and standard errors based on precision weighting because of our diversity in block  size (see Hansen and Bowers 2008 among other places showing the precision gains from this approach).

## Approaches to Testing

We will use both direct permutation  based approaches to testing as well as asymptotic approaches since we have only 16 "treated" clusters.

We will also use both differences of means as  test statistics as well as rank-based test statistics given our small sample.

## Approach to multiple testing

We have 8 outcomes and one comparison (Selling versus Not Selling pharmacy). If
we were going to make a decision about the effect of the pharmacies if *any one
of the 8 comparisons yielded a p<.05*  then  we would make a false positive
error not 1 in 20 tests, but $1 − (1 − .05)^8 \approx 1/3$  or almost 7/20.

However,  if each analysis stands alone in terms of our  decision making : the
assessment of perceptions of insecurity can be null  or significant
independently of the assessment of reports of experiences with crime, then we
do not need to adjust the tests.

In the case of this project, we do not make any adjustment because decisions
regarding the effect of the pharmacy stand alone.

## Covariates for covariance adjustment

We are matching to balance covariates measured at both individual level as well as at the neighborhood level (including both aggregates of the individual survey level measures and administrative data). Yet, we do not make person-to-person sets across neighborhood strata. For this reason, and also following Rubin and Thomas, 1991, we adjust our estimates of average effects and our tests following Rosenbaum 2002 using the following short list of background covariates.

```r
covariates <- c("ideol_si_i","educ_i","sex_i","age_i")
```

# Missing  Data  and Extreme Data Points

Since our data are from a survey we do not anticipate extreme data points in the endline --- our  work with the baseline  data supports this idea that we should not worry about overly influential points 


### Statistical Inferencea

We will estimate the average effect of living near a pharmacy that sells
marijuana using differences of means conditional on matched set, adjusting the
standard errors for hypothesis testing and confidence interval creation using
the CR2 cluster-robust standard errors (cite). All of this will occur using the
`lm_robust()` command from the `estimatr` package in R.

```{r eval=FALSE}

lm1 <- lm_robust(outcome1~soldvsnot17,fixed_effects=~fm_i,cluster=Q56,data=dat17i)


```


### Sensitivity Analysis

We will conduct a sensitivity analysis using both the Rosenbaum style approach
(probably using the `senstrat` package for R) and the Cinelli and Hazlett
approach (using the `sensmakr` package for R).



# References
