---
title: Initial Balance Assessment before Matching
author: Jake Bowers
date: '`r format(Sys.Date(), "%B %d, %Y")`'
fontsize: 11pt
geometry: margin=1in
graphics: yes
indent: false
bibliography:
 - ../refs.bib
biblio-style: authoryear-comp
output:
  pdf_document:
    toc: true
    number_sections: true
    fig_caption: yes
    fig_height: 4
    fig_width: 4
    latex_engine: xelatex
    keep_tex: true
    citation_package: biblatex
    md_extensions: +raw_attribute
---

```{r echo=FALSE, include=FALSE, cache=FALSE}
library(here)
source("rmarkdownsetup.R")
library(dplyr)
library(coin)
library(RItools)
```

```{r}
load(here::here("Analysis","match_data_prep.rda"))
```

### Look at baseline imbalance before matching

The following analysis shows that the neighborhoods with and without marijuana
selling pharmacies are quite similar on the covariates listed below. Below we
show the standardized differences (differences in means in standard deviation
units) and $p$-values for a test of the null of no difference in means between
the registered pharmacies and the non-registered pharmacies.


First, drop the observations for the placebo pharmacies
```{r}
dat17i <- wdat17i %>% filter(!is.na(soldvsnot17))
table(dat17i$soldvsnot17,exclude=c())

```
Looking at baseline (im)balance on individual level outcomes and covariates

```{r eval=FALSE}
baselineFmla <- reformulate(covs3, response = "soldvsnot17")
baselineFmlaCluster <- update(baselineFmla, . ~ . + cluster(Q56))

xb0i <- balanceTest(baselineFmlaCluster, data = dat17i, report = "all", p.adjust.method = "none")
xb0i$overall[, ]
xb0ionebyone <- data.frame(xb0i$results[,,])
xb0ionebyone$varnm <- row.names(xb0ionebyone)
xb0ionebyone <- xb0ionebyone %>% arrange(desc(abs(std.diff)))
xb0ionebyone <- xb0ionebyone %>% filter(varnm!="(_non-null record_)")
## head(xb0ionebyone,n=20) ## Worst balanced
## Number of small p-values
numsmallp1 <- sum(xb0ionebyone[, "p"] <= .05)

##xb0itest <- balanceTest(baselineFmla, data = wdat17, report = "all", p.adjust.method = "none")
##xb0itest$overall[,]
```

```{r eval=FALSE}
summary(xb0ionebyone$std.diff)

adjps <- p.adjust(xb0ionebyone$p,method="holm")
```

Add informative labels.

```{r eval=FALSE}
xb0ionebyone$thevar <- 1:nrow(xb0ionebyone)
xb0ionebyone$varlab <- c(
"Violent robberies",
"Physical Disorder- trash in the street ",
"Security Measures: Security Camera",
"Mean age",
"Physical Disorder- Potholes/Wells in the street",
"Total population of the segment",
"Robberies",
"Security Measures: alarm response",
"Mvd - Rest of the country",
"Votes for P.N. (%)",
"Average of years of education",
"Percentage of votes to Frente Amplio (2014)",
"Homes with defenses/bars",
"Percentage of votes to Partido de los Trabajadores (2014)",
"Perception of Insecurity in neighborhood",
"Votes for PERI (%)",
"Percentage of votes to Asamblea Uruguay (2014)",
"Victimization - Last 12 Months",
"Votes for P.C. (%)",
"Frequency of activities in the neighborhood - Meets/ organizes with the neighbors for any improvement activity for the neighborhood",
"Public stigma - Agreement: Most people feel that using marijuana is a sign of personal failure",
"Homeowners(%)",
"Public stigma - Agreement: Most employers do not hire a person who uses marijuana",
"ubn_no",
"Country insec. perception",
"Percentage of homes with NONE UBN",
"Public Stigma Factor ",
"Votes for P.I. (%)",
"Security Measures: Guard at night",
"Agreement with the sale of marijuana for recreative use in pharmacies",
"People who use marijuana are a threat to society",
"Frequency of activities in the neighborhood - purchase in shops or shops in the neighborhood",
"Public stigma - Agreement: Most people believe that marijuana users are dangerous",
"Agreement - although they regulate, people will continue buying marijuana illegal",
"Social disorder -  People drunk or stoned in the streets",
"Agreement - The legalization of marijuana will contribute to solve social problems",
"Frequency of activities in the neighborhood -  Talk with your neighbors",
"Public stigma - Agreement: Most employers do not hire a person who uses marijuana",
"Impact of the Law - Public Health",
"Sex",
"Number of offenses",
"Impact of the law - Public Safety",
"Homes with 3 or more UBNs(%)",
"Social disorder -  people discussing in aggressive or violent",
"Impact of the law - Individual Freedoms",
"Public stigma - Most people believe that you cannot trust marjuana user",
"Percentage of Renters",
"Stigmatization Factor",
"Stigmatization Agreement: Marijuana Users are dishonest",
"neigh4_i sacle from 0 to 1",
"Social disorder index",
"Stigmatization Agreement: Most marijuana users are not well educated",
"Agreement - The legalization of marijuana will prevent the consumption of drugs more dangerous",
"Perception of risk - Try marijuana once or twice in a lifetime",
"Public stigma - Most people do not take seriously the views of a marijuna user",
"Agreement with the decriminalization and regulation by the state of the market of marijuana",
"Type of crime",
"Risk perception of frequent marijuana use",
"Frequency of activities in the neighborhood -  buy at the pharmacy in the neighborhood",
"Valor Catastral 2017 ($)",
"Age",
"Density population of the segment",
"Social disorder -  young people or children in the streets without doing anything, who are wandering",
"Perceived impact on drug trafficking",
"Agreement - marijuana is the gateway to other drugs such as cocaine, LSD and base paste",
"Prevalence of consumption - at some point in their lives.",
"Contact with marijuana consumers",
"Public stigma - Agreement: Most people feel that using marijuana is a sign of personal failure",
"Frequency of activities in the neighborhood - Use health services",
"Public stigma - Most people would treat marijuana users as any person ",
"Security Measures: 222 Service or security guard during the day",
"Perception of risk - Using marijuana occasionally",
"Citizens insertion in the neighborhood",
"Public stigma - Agreement: Most people would not accept a marijuana user as a high school teacher",
"Agreement - Using marijuana is harmful to health ",
"Highest educational level",
"Stigmatization Agreement: marijuana users make me mad",
"neigh8_i sacle from 0 to 1",
"Self-ideology identification",
"Percentage of homes with TWO UBNs",
"Public stigma - Agreement: Most people underestimate marijuana users"
)

#age_av	Mean age
#robb_2016	Number of robberies
#pn_per	Votes for Partido Nacional (%)
#dis3_i	Homes that have defenses/metal grilles or bars on the windows (includes perimeter fence, barbed wire, and similar)
#peri_per	Votes for PERI (%)
#pc_per	Votes for Partido Colorado (%)
#h_owners	Percentage of homeowners
#c_sec_i	Country insecurity perception
#pi_per	Votes for Partido Independiente (%)
#op6_m_i	Agreement - The people who use marijuana are a threat to society
#op5_m_i	Agreement - although they regulate, people will continue buying marijuana illegal
#neigh2_i	Frequency of activities in the neighborhood -  Talk with your neighbors
#sex_i	Sex
#ubn_more	Percentage of homes with THREE OR MORE UBNs
#pstigma1_i	Public stigma - Agreement: Most people believe that you cannot trust marjuana user
#stigma6_i	Stigmatization Agreement: Marijuana Users are dishonest
#stigma1_i	Stigmatization Agreement: Most marijuana users are not well educated
#pstigma6_i	Public stigma - Agreement: Most people do not take seriously the views of a marijuna user
#rp_m3_i	Risk perception of frequent marijuana use
#age_i	Age
#dt_impact_i	Perceived impact on drug trafficking
#ffuse_i	Contact with marijuana consumers
#pstigma5_i	Public stigma - Agreement: Most people would treat marijuana users as any person 
#activities_index	Citizens insertion in the neighborhood
#educ_i	Educational level
#ideol_si_i	Ideological self-identification
```

Make the  plot

```{r}

xb0ionebyone$abs_std_diff <- abs(xb0ionebyone$std.diff)


is_outlier <- function(x,mult=1.5,pos_only=TRUE) {
	if(!pos_only){
  return(x < quantile(x, 0.25) - mult * IQR(x) | x > quantile(x, 0.75) + mult * IQR(x))
	} else {
  return( x > quantile(x, 0.75) + mult * IQR(x))
  }
}

dat <- xb0ionebyone %>% mutate(is_outlier=ifelse(is_outlier(abs_std_diff,.1), abs_std_diff, as.numeric(NA)))
dat$varlab[which(is.na(dat$is_outlier))] <- as.numeric(NA)
dat$varlab

pdf(file=here::here("media","initial_balance_plot.pdf"),width=4,height=8)

par(oma=rep(0,4)+.01,mar=c(3,8,0,0),mgp=c(1,.5,0))

g  <- ggplot(data=dat,aes(y=abs_std_diff,x="",label=varlab))+
	geom_boxplot(outlier.shape=NA)+
	#geom_point(aes(x=1)) +
	theme_bw() +
	ylab("Abs(Standardized Mean Differences, Pharmacy - No-Pharmacy)") + 
	xlab("")
fullg  <- g + geom_text(aes(label=varlab),na.rm=TRUE,nudge_y=0.05,size=3)
print(fullg)

dev.off()

## with(xb0ionebyone,{
## 	     plot(abs(std.diff),thevar,
## 		       pch=21,
## 		       xlab="Absolute Std. Diff of Means",ylab="",
## 		       bg=c("white","black")[as.numeric(xb0ionebyone$p<=.05)+1],
## 		       axes=FALSE)
## axis(1)
## axis(2,at=thevar,labels=varlab,las=2,tick=FALSE)
## segments(rep(0,nrow(xb0ionebyone)),thevar,abs(std.diff),thevar,lwd=.5,col="gray")
## }
## )


```


Relationship between pharmacies and baseline perception of risk:

```{r}
table(dat17i$treat, dat17i$n_sec_i, exclude = c())
```

```{r}
boxplot(n_sec_i ~ treat, data = dat17i)
stripchart(n_sec_i ~ treat, data = dat17i, vertical = TRUE, add = TRUE)
```


@hansen2008cbs suggested that an observational study could be judged, in part,
by comparing it to a randomized experimental study of the same covariates and
design. The preceding test makes this comparison. If we had randomly assigned
pharmacies to register to sell marijuana and we had assessed treatment versus
control mean differences in 100 variables, we would have expected 5 variables
to have $p$ less than .05 **just through chance**.  That is, 5 small p-values
out of 100 would not impugn the design of an experiment --- in fact it would be
expected. In this case, we see `r numsmallp1` such small $p$-values ---
suggesting an overall inconsistency with the experimental standard (not
surprising since this is observational data). The omnibus or overall $p$ above
attempts to direct attention away from the individual p-values and to focus on
the collection of differences. And, we could also have used a multiple testing
adjustment for the p-values (which would show no statistically significant
differences).

We can also show that, using unadjusted p-values, that these
covariates-to-marijuana selling relationships depart somewhat from the patterns
of a randomized design by just counting up the number of significant p-values
and comparing that number to the expected number under a randomized design.


```{r}
## It looks pretty balanced at least on means!
## Recall the number of p-values less than .05 that we'd expect by chance:
nrow(xb0ionebyone) * .05
sum(xb0ionebyone[, "p"] <= .05)
## So perhaps some imbalance but not a lot.
```

Save products

```{r}

save(xb0i, baselineFmla, baselineFmlaCluster, file="initial_balance.rda")

```


## References
