---
title: Initial Balance Assessment before Matching
author: Jake Bowers
date: '`r format(Sys.Date(), "%B %d, %Y")`'
fontsize: 11pt
geometry: margin=1in
graphics: yes
indent: false
bibliography:
 - ../refs.bib
biblio-style: authoryear-comp
output:
  pdf_document:
    toc: true
    number_sections: true
    fig_caption: yes
    fig_height: 4
    fig_width: 4
    latex_engine: xelatex
    keep_tex: true
    citation_package: biblatex
    md_extensions: +raw_attribute
---

```{r echo=FALSE, include=FALSE, cache=FALSE}
source("rmarkdownsetup.R")
```

```{r}
load(here::here("Analysis","match_data_prep.rda"))
```

### Look at baseline imbalance before matching

The following analysis shows that the neighborhoods with and without marijuana
selling pharmacies are quite similar on the covariates listed below. Below we
show the standardized differences (differences in means in standard deviation
units) and $p$-values for a test of the null of no difference in means between
the registered pharmacies and the non-registered pharmacies.


First, drop the observations for the placebo pharmacies
```{r}
dat17i <- wdat17i %>% filter(!is.na(soldvsnot17))
table(dat17i$soldvsnot17,exclude=c())

```
Looking at baseline (im)balance on individual level outcomes and covariates

```{r}
baselineFmla <- reformulate(covs3, response = "soldvsnot17")
baselineFmlaCluster <- update(baselineFmla, . ~ . + cluster(Q56))

xb0i <- balanceTest(baselineFmlaCluster, data = dat17i, report = "all", p.adjust.method = "none")
xb0i$overall[, ]
xb0ionebyone <- data.frame(xb0i$results[,,])
xb0ionebyone$varnm <- row.names(xb0ionebyone)
xb0ionebyone <- xb0ionebyone %>% arrange(desc(abs(std.diff)))
xb0ionebyone
## head(xb0ionebyone,n=20) ## Worst balanced
## Number of small p-values
numsmallp1 <- sum(xb0ionebyone[, "p"] <= .05)

##xb0itest <- balanceTest(baselineFmla, data = wdat17, report = "all", p.adjust.method = "none")
##xb0itest$overall[,]
```

```{r}
summary(xb0ionebyone$std.diff)

adjps <- p.adjust(xb0ionebyone$p,method="holm")
```

```{r}
xb0ionebyone$thevar <- 1:nrow(xb0ionebyone)
xb0ionebyone$varlab <- c(
"Violent robberies",
"dis1_i",
"sec_mea3_p",
"Mean age",
"dis2_i",
"pop",
"Robberies",
"sec_mea1_p",
"mvd_int",
"Votes for P.N. (%)",
"educ_av",
"fa_per",
"Homes with defenses/bars",
"pt_per",
"n_sec_i",
"Votes for PERI(%)",
"ap_per",
"vic12_i",
"Votes for P.C.(%)",
"neigh3_i",
"pstigma3_i",
"Homeowners(%)",
"pstigma4_i",
"ubn_no",
"Country insec. perception",
"ubn_one",
"ps1718",
"Votes for P.I.(%)",
"sec_mea4_p",
"law2_i",
"People who use marijuana are a threat to society",
"neigh6_i",
"pstigma2_i",
"Agreement - although they regulate, people will continue buying marijuana illegal",
"dis5_i",
"op3_m_i",
"Frequency of activities in the neighborhood -  Talk with your neighbors",
"stigma4_i",
"ph_impact_i",
"Sex",
"vic12_n_i",
"ps_impact_i",
"Homes with 3 or more UBNs(%)",
"dis6_i",
"if_impact_i",
"Public stigma - Most people believe that you cannot trust marjuana user",
"rent_per",
"st1718",
"Stigmatization Agreement: Marijuana Users are dishonest",
"neigh4_i",
"social_dis",
"Stigmatization Agreement: Most marijuana users are not well educated",
"op4_m_i",
"rp_m1_i",
"Public stigma - Most people do not take seriously the views of a marijuna user",
"law1_i",
"crime_t_i",
"Risk perception of frequent marijuana use",
"neigh7_i",
"cat_value",
"Age",
"dens",
"dis4_i",
"Perceived impact on drug trafficking",
"op2_m_i",
"prev_lt_i",
"Contact with marijuana consumers",
"stigma3_i",
"neigh5_i",
"Public stigma - Most people would treat marijuana users as any person ",
"sec_mea2_p",
"rp_m2_i",
"Citizens insertion in the neighborhood",
"pstigma8_i",
"op1_m_i",
"educ_i",
"stigma2_i",
"neigh8_i",
"ideol_si_i",
"ubn_two",
"pstigma7_i"
)

#age_av	Mean age
#robb_2016	Number of robberies
#pn_per	Votes for Partido Nacional (%)
#dis3_i	Homes that have defenses/metal grilles or bars on the windows (includes perimeter fence, barbed wire, and similar)
#peri_per	Votes for PERI (%)
#pc_per	Votes for Partido Colorado (%)
#h_owners	Percentage of homeowners
#c_sec_i	Country insecurity perception
#pi_per	Votes for Partido Independiente (%)
#op6_m_i	Agreement - The people who use marijuana are a threat to society
#op5_m_i	Agreement - although they regulate, people will continue buying marijuana illegal
#neigh2_i	Frequency of activities in the neighborhood -  Talk with your neighbors
#sex_i	Sex
#ubn_more	Percentage of homes with THREE OR MORE UBNs
#pstigma1_i	Public stigma - Agreement: Most people believe that you cannot trust marjuana user
#stigma6_i	Stigmatization Agreement: Marijuana Users are dishonest
#stigma1_i	Stigmatization Agreement: Most marijuana users are not well educated
#pstigma6_i	Public stigma - Agreement: Most people do not take seriously the views of a marijuna user
#rp_m3_i	Risk perception of frequent marijuana use
#age_i	Age
#dt_impact_i	Perceived impact on drug trafficking
#ffuse_i	Contact with marijuana consumers
#pstigma5_i	Public stigma - Agreement: Most people would treat marijuana users as any person 
#activities_index	Citizens insertion in the neighborhood
#educ_i	Educational level
#ideol_si_i	Ideological self-identification



pdf(file=here::here("media","initial_balance_plot.pdf"))

par(oma=rep(0,4)+.01,mar=c(3,8,0,0),mgp=c(1,.5,0))
with(xb0ionebyone,{
	     plot(abs(std.diff),thevar,
		       pch=21,
		       xlab="Absolute Std. Diff of Means",ylab="",
		       bg=c("white","black")[as.numeric(xb0ionebyone$p<=.05)+1],
		       axes=FALSE)
axis(1)
axis(2,at=thevar,labels=varlab,las=2,tick=FALSE)
segments(rep(0,nrow(xb0ionebyone)),thevar,abs(std.diff),thevar,lwd=.5,col="gray")
}
)




dev.off()


```


Relationship between pharmacies and baseline perception of risk:

```{r}
table(dat17i$treat, dat17i$n_sec_i, exclude = c())
```

```{r}
boxplot(n_sec_i ~ treat, data = dat17i)
stripchart(n_sec_i ~ treat, data = dat17i, vertical = TRUE, add = TRUE)
```


@hansen2008cbs suggested that an observational study could be judged, in part,
by comparing it to a randomized experimental study of the same covariates and
design. The preceding test makes this comparison. If we had randomly assigned
pharmacies to register to sell marijuana and we had assessed treatment versus
control mean differences in 100 variables, we would have expected 5 variables
to have $p$ less than .05 **just through chance**.  That is, 5 small p-values
out of 100 would not impugn the design of an experiment --- in fact it would be
expected. In this case, we see `r numsmallp1` such small $p$-values ---
suggesting an overall inconsistency with the experimental standard (not
surprising since this is observational data). The omnibus or overall $p$ above
attempts to direct attention away from the individual p-values and to focus on
the collection of differences. And, we could also have used a multiple testing
adjustment for the p-values (which would show no statistically significant
differences).

We can also show that, using unadjusted p-values, that these
covariates-to-marijuana selling relationships depart somewhat from the patterns
of a randomized design by just counting up the number of significant p-values
and comparing that number to the expected number under a randomized design.


```{r}
## It looks pretty balanced at least on means!
## Recall the number of p-values less than .05 that we'd expect by chance:
nrow(xb0ionebyone) * .05
sum(xb0ionebyone[, "p"] <= .05)
## So perhaps some imbalance but not a lot.
```

Save products

```{r}

save(xb0i, baselineFmla, baselineFmlaCluster, file="initial_balance.rda")

```


## References
