---
title: Estimate causal effects and test hypotheses about the causal effects of the pharmacies on attitudes and perceptions
author: Jake Bowers
date: '`r format(Sys.Date(), "%B %d, %Y")`'
fontsize: 11pt
geometry: margin=1in
graphics: yes
indent: false
bibliography:
 - ../refs.bib
biblio-style: authoryear-comp
output:
  pdf_document:
    toc: true
    number_sections: true
    fig_caption: yes
    fig_height: 4
    fig_width: 4
    latex_engine: xelatex
    keep_tex: true
    citation_package: biblatex
    md_extensions: +raw_attribute
---


```{r echo=FALSE, include=FALSE, cache=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).
# knitr settings to control how R chunks work.
rm(list=ls())

require(knitr)

## This plus size="\\scriptsize" from https://stackoverflow.com/questions/26372138/beamer-presentation-rstudio-change-font-size-for-chunk

knitr::knit_hooks$set(mysize = function(before, options, envir) {
			      if (before){
				      return(options$size)
			      } else {
				      return("\\normalsize")
			      }

})

knit_hooks$set(plotdefault = function(before, options, envir) {
		       if (before) par(mar = c(3, 3, .1, .1),oma=rep(0,4),mgp=c(1.5,.5,0))
})

opts_chunk$set(
	       tidy='styler',     # display code as typed
	       echo=TRUE,
	       results='markup',
	       strip.white=TRUE,
	       fig.path='figs/fig',
	       cache=FALSE,
	       highlight=TRUE,
	       width.cutoff=132,
	       size='\\scriptsize',
	       out.width='.8\\textwidth',
	       fig.retina=FALSE,
	       message=FALSE,
	       comment=NA,
	       mysize=TRUE,
	       plotdefault=TRUE)

options(digits=4,
	scipen=8,
	width=132
)
```


```{r setup1, echo=FALSE}
## Later make this installation to a local library
### This next will not re-run if there has not been change in Github
devtools::install_github("markmfredrickson/RItools") 
library(RItools)
library(optmatch)
library(here)
library(tidyverse)
library(arm)
library(estimatr)
library(clubSandwich)
```


```{r makedirs, echo=FALSE, include=FALSE}
if(!dir.exists('figs')) dir.create('figs')

## Make a local library directory
if(!dir.exists(here::here('libraries'))){
        dir.create(here::here('libraries'))
}
```

```{r loadmatchingresults}
load("matchingresults.rda",verbose = TRUE)
```

This file asks whether and how the presence of a pharmacy might have had an
effect on the perceptions and/or attitudes of neighbors.

## Outcomes


"ps1718" "st1718" "law1_i" "law2_i" "n_sec_i" "c_sec_i" "ph_impact_i" "ps_impact_i" "dt_impact_i" "if_impact_i" "rp_m2_i" "crime_t_i" "op4_m_i" "op5_m_i" "op6_m_i"

Also an index of activities performed by neighbors in their neighborhood: "neigh2_i" "neigh3_i" "neigh4_i" "neigh5_i" "neigh6_i" "neigh7_i" "neigh8_i".

And a social disorder index: "dis4_i" "dis5_i" "dis6_i".

Outcomes
 - Neighborhood insecurity perception: n_sec_i
 - Country insecurity perception: c_sec_i
 - Crime victimization: vic12
 - Percieved impact on drug trafficking: dt_impact_i
 - Percieved impact on public safety: ps_impact_i
 - Presence of illegal selling ponits "bocas": boca1_i

Covariates for covariance adjustment in addition to matching:
 - Ideology: ideol_si_i
 - Education: educ_i
 - Sex: sex_i
 - Age: age_i

```{r}

outcomes <- c("n_sec_i","c_sec_i","vic12","dt_impact_i","ps_impact_i","boca1_i")
covariates <- c("ideol_si_i","educ_i","sex_i","age_i")

allvars <- c(outcomes,covariates)

summary(wrkdat2[,allvars])

allvars[!(allvars %in% names(wrkdat2))]
allvars[!(allvars %in% names(finaldat))]


```


## Design

We created a matched design using an optimal, full matching algorithm.

```{r}

summary(fm2,min.controls=0,max.controls=Inf,data=datphm)

```

These designs compare favorably to what we would expect to see from an equivalent block-randomized experiment.

```{r}

xb2fm$overall[,]

```

## Analysis

This study can be thought of as a block and cluster randomized experiment with
neighborhoods as clusters assigned to a pharmacy within blocks defined by
background covariates. The clusters are not all the same size, so we need to
adjust for biases arising from this problem (Middleton and Aronow). And we need
to be aware of problems of p-values as well.


## Results

Here we save results to be used in tables and figures and in the text itself.



