---
title: Pre-analysis plan and design description
author: Jake Bowers
date: '`r format(Sys.Date(), "%B %d, %Y")`'
fontsize: 11pt
geometry: margin=1in
graphics: yes
indent: false
bibliography:
 - ../refs.bib
biblio-style: authoryear-comp
output:
  pdf_document:
    toc: true
    number_sections: true
    fig_caption: yes
    fig_height: 4
    fig_width: 4
    latex_engine: xelatex
    keep_tex: true
    citation_package: biblatex
    md_extensions: +raw_attribute
---

```{r echo=FALSE, include=FALSE, cache=FALSE}
library(here)
source(here::here("Analysis","rmarkdownsetup.R"))
```

```{r setup1, echo=TRUE}
library(RItools)
library(optmatch)
library(tidyverse)
library(arm)
library(tidyverse)
library(formula.tools)
library(coin)
load(here::here("Analysis","match_data_prep.rda"),verbose=TRUE)
load(here::here("Analysis","initial_balance.rda"),verbose=TRUE)
##  First, drop the observations for the placebo pharmacies

table(wdat17i$soldvsnot17,exclude=c())
table(wdat17p$soldvsnot17,exclude=c())

dat17i <- wdat17i %>% filter(!is.na(soldvsnot17))
table(dat17i$soldvsnot17,exclude=c())

dat17p <- wdat17p %>% filter(!is.na(soldvsnot17))
table(dat17p$soldvsnot17,exclude=c())

load(here::here("Analysis","design_soldvsnot.rda"),verbose=TRUE)
```

We aim to assess the effect of living near a pharmacy that sells marijuana on
the attitudes and perceptions of the neighbors after living near that selling
pharmacy for one year. We are focusing on neighbors' perceptions of crime and
experiences with crime as outcomes in this study.

# Study Design Overview: Data Collection


## Data Collection: Changes in Selling Pharmacies

Our initial sample contained 42 non-selling pharmacies and 18 selling ones.
Figure \ref{fig:ctrltrtpharms_1} shows the geographical distribution of the
pharmacies in our study. During the first year of policy implementation, some
changes in the pharmacies selling group occurred. First, two pharmacies that
initially were registered to sell, never actually did it: this reduced our
selling group to 16. Second, six pharmacies that had entered the system
abandoned it due to the prohibition imposed by US banks that forbid cannabis
selling pharmacies to operate with bank accounts.\footnote{For information about
the problem with the banking system see:
\url{https://www.elobservador.com.uy/nota/brou-cierra-cuentas-vinculadas-con-marihuana-y-mas-farmacias-evaluan-dejar-de-venderla-20178175004}.}
And third, because pharmacy registration remained open, 4 new pharmacies entered
the system.

This means that by the second round of data collection we had (1) pharmacies
that never sold and never registered to do it (n=42) that we call ``control'' or
``comparison'' pharmacies, (2) two pharmacies that never sold but initially were
willing to do it (n=2) named as ``placebo'' pharmacies, (3)  pharmacies that
sold cannabis during the entire time between the first and second round (n=10)
that we label as ``wholetime'', (4) pharmacies that sold marijuana for some of
that first year but stopped selling at some point between 2017 to 2018 (n=6)
that we call ``dropouts'', and (5) pharmacies that joined the system at some
point between the 2017 round and 2018 round (n=4) that we call ``newcomers''
(see Table \ref{tab:pharmsalestatus} in APPENDIX TODO).

\begin{figure}[htpb!]
    \centering
    \label{fig:ctrltrtpharms_1}
    \caption{Pharmacies registered to sell marijuana and comparison pharmacies}
    \includegraphics[width=6.5in,height=3.4851in]{../media/country.png}
\footnotesize{Note: green symbols show pharmacies registered to sell marijuana as of June 2017. \\ Blue symbols are comparison pharmacies.}
\end{figure}

The comparison group of pharmacies was selected following four criteria that
aimed to produce a set of pharmacies that was not selling cannabis where the
neighborhood characteristics would be at least roughly similar to the
neighborhood characteristics of the selling pharmacies.  Here we describe
the first steps in our selection process. The first criteria was ``same
geographical unit'':  pharmacies in the same administrative region (the
``departamento'') without at least one selling pharmacy were deleted from the
sampling frame. The second criteria was ``population density'':  pharmacies in
rural areas were deleted from the sample because none of the selling pharmacies
is located in rural areas. The third criteria was``criminality rate'':
pharmacies in neighborhoods (for Montevideo) or cities where homicides reports,
assaults reports and robberies reports are too high or too low  in comparison
with the neighborhoods where selling pharmacies were situated, were discarded.
The fourth criteria is ``distance'': pharmacies in the control group should be
at least 6 blocks away from any treatment pharmacy. After eliminating the
pharmacies that did not pass the four criteria, we randomly selected 42 control
pharmacies among the about 1000 pharmacies that exist in the country
\footnote{We used official sociodemographic information about the
neighbourhoods/localities/``departamentos''. See Table \ref{tab:phlongtable} in
Appendix A for more details on the pharmacies characteristics}.

\begin{small}
\begin{table}[htbp!]
\scriptsize
  \centering
   \caption{Status of  marijuana selling pharmacies}
  \label{tab:pharmsalestatus}
  \begin{tabular}{@{}lllcccccc@{}}
\textbf{Pharmacy}  &  \textbf{Neighborhood}  &  \textbf{Dpt.}  &  \textbf{Round 1}  &  \textbf{Round 2}  &  \textbf{Entrance}  &  \textbf{Drop out}  &  \textbf{Type}  \\
\midrule
Antartida     &     Centro     &     Montevideo     &     Yes     &     Yes     &     7/19/17     &        &     wholetime  \\
 Caceres      &     Pocitos     &     Montevideo     &     Yes     &     Yes     &     7/19/17     &        &     wholetime  \\
 Tapie     &     Ciudad vieja     &     Montevideo     &     Yes     &     Yes     &     7/19/17     &      &     wholetime  \\
 Las toscas     &     Las toscas     &     Canelones     &     Yes     &     Yes     &     7/19/17     &      &     wholetime  \\
 Nueva Brun     &     Trinidad     &     Flores     &     Yes     &     Yes     &     7/19/17     &        &     wholetime  \\
 Gortari     &     Centro     &     Lavalleja     &     Yes     &     Yes     &     7/19/17     &        &     wholetime  \\
 La Cabina     &     Las Flores     &     Maldonado     &     Yes     &     Yes     &     7/19/17     &      &     wholetime  \\
 Termal guaviyu     &     Termas     &     Paysandú     &     Yes     &     Yes     &     7/19/17     &      &     wholetime  \\
 Albisu Termal     &     Pasaje Comercial    &   Salto  &     Yes     &     Yes     &     7/19/17     &     &     wholetime  \\
 Bengoechea     &     Centro     &     Tacurembó     &     Yes     &     Yes     &     7/19/17     &        &     wholetime  \\
 Miguel     &     Canelones centro   &    Canelones   &   Yes     &   Yes     &   7/19/17     &  10/2/17     &     dropouts  \\
 Carmelo     &     Carmelo     &     Colonia     &     Yes     &     Yes     &     7/19/17     &   8/25/17     &     dropouts  \\
 Pitagoras     &     Malvin norte     &     Montevideo     &     Yes     &     Yes     &    7/19/17     &     8/9/17     &     dropouts  \\
 Saga     &     Centro     &     Artigas     &     Yes     &     Yes     &     7/19/17     &   9/6/17     &     dropouts  \\
 Medicci     &     Paysandú     &     Paysandú     &     Yes     &     Yes     &   7/19/17     &     9/1/17     &     dropouts  \\
 Bidegain     &     Libertad     &     San José     &     Yes     &     Yes     &    7/19/17     &     9/1/17     &     dropouts  \\
 Camaño     &     Pocitos     &     Montevideo     &     No     &     Yes     &    9/11/17     &          &     newcomers  \\
 Silleda     &     Brazo oriental     &     Montevideo     &     No     &     Yes     &     9/11/17     &          &     newcomers\\
 Constitución Sur     &     Flor de Maroñas     &     Montevideo     &     No     &     Yes     &     20/4/18     &          &     newcomers  \\
 Lilen     &     Punta Carretas     &     Montevideo     &     No     &     Yes     &     17/5/18     &          &     newcomers  \\
\bottomrule
\end{tabular}
\end{table}
\end{small}

For this study we are interested in the effects of living near a pharmarcy that
sold marijuana for at least part of the period. Since we did not have baseline
data for the ``newcomer'' pharmacies, we do not use them in our analysis as
described here. We combine the ``wholetime'' and ``dropout'' pharmacies as our
``selling'' group (16 pharmacies) and use the 42 comparison pharmacies which
never sold marijuana as the source of our comparison group. We describe more
below about how we designed our specific comparisons after we describe the
survey data collection that measured attitudes about marijuana before and after
the pharmacies began sales.

\subsection{Neighbors Survey}

The data used in this analysis come from face-to-face surveys that aimed to help
us measure the crime victimization experienced by those living near pharmacies
and their attitudes towards the law and public security. None of these surveys
were intended to be representative of the Uruguayan population. We conducted two
rounds of surveys with neighbors of selling and non-selling pharmacies. In
collaboration with TODO GOVERNMENT GROUP, our research team learned the names
and locations of the pharmacies that were going to sell marijuana as of the date
that the law allowing sales at pharmacies went into effect (July 19, 2017). In the
first survey round, fieldwork started on June 17, 2017 and finished in July 1,
2017 before the sales started. The sample contains 600 neighbors
of 60 pharmacies, 10 neighbors per pharmacy. The list of pharmacies that were
licensed to sell marijuana was confidential until the sale started, so this initial group of
neighbors did not know if their closest pharmacy was going to sell.

The second round of the survey was carried out approximately one year later,
between August 9 and September 30, 2018. Overall, we have conducted 1298
interviews across the country in the two rounds. Respondents were selected among
people over 18 years old that lived in the sampled household and were present at
the moment of the interview. The most recent birthday selection process was used
to choose among households residents.

\subsection{Pharmacy Interviews}

In addition to neighbors, we also interviewed one representative of each
pharmacy (sellers and non-sellers) in both rounds. Overall, we conducted 119
surveys with pharmacy representatives (59 in 2017 and 60 en 2018).  Data from
the pharmacies' representatives survey allowed us to characterize selling and
non-selling pharmacies, and to describe any initial differences
between them using the 2017 data.

The data that we collected (as described in TODO APPENDIX) show that selling and
non-selling pharmacies are not different in terms of their general
characteristics: TODO explain a bit more. The only relevant distinction is that
among non-selling there are stores that are part of a larger pharmacy's chain.
In terms of infrastructure both selling and non-selling pharmacies are quite
similar, and they are also similar regarding security measures, perceptions of
security by their workers (the representatives of the pharmacy who spoke with
our interviewer) and crime victimization. These data suggest that pharmacies
that sell cannabis did so not because they are better equipped in terms of
security protection, have suffered less crimes and/or feel more secure in their
neighborhoods. We also did not detect large differences between the ways that
pharmacy repesentatives thought about cannabis and its users (TODO see
Table/Figure TODO in Appendix).

The most important distinction among sellers and non-sellers is concerning
opinions towards the public policy itself. Owners and representatives of pharmacies
that decided to sell are consistently more in favor of the regulation and
anticipate it would have more positive impacts TODO ON SOCIETY? (Table
\ref{tab:pharmaciesperceptions} in Appendix A).

## The Stratification Design

To learn about whether sale of cannabis in pharmacies influences crime
victimization, attitudes and perceptions of neighbors, we compare the survey
responses of neighbors living near pharmacies selling cannabis to the responses
of neighbors who did not live near such pharmacies. The problem arising from a
strategy like this, is that neighborhoods where pharmacy owners decided to sell
cannabis are probably different from neighborhoods where they decided to pass
over the opportunity to sell cannabis (we already know that owners and
representatives of the pharmacies differ on their opinions towards the policy
even if the pharmacies themselves were not overly different in most other
aspects see TODO Table in Appendix). The question is whether the amount of
difference between the two groups of pharmacies would mislead us as we interpret
such comparisons. What is the standard to judge whether a given comparison
people living near selling to non-selling pharmacies might mislead us? We know
that if an intervention is randomly assigned, then the comparisons based on that
intervention would not confuse causal effects with confounding. That is, we know
that, say, if we were to randomly assign licenses to sell marijuana to 16 out of
60 pharmacies, those 16 pharmacies and their surrounding neighborhoods might
well differ, but those differences would not be systematically related to the
decision to sell marijuana, and thus not systematically related to the exposure
of people nearby to the selling of marijuana. Now, we do not have such a
randomized design, but we know what such a design would look like. And we can
use the hypothetical design as a standard against which we can compare an
observational study. [@hansen2008cbs] develop a formal way to compare a
given observed comparison with what would be expected if that comparison had
been randomized: they provide a test for the hypothesis
that the neighbors of selling pharmacies and the neighbors of not selling
pharmacies might have been allocated at random. In our case, the raw comparison
of attitudes around pharmacies selling cannabis and those not selling cannabis,
confirms our hunch that the places do not in fact compare favorably to a
randomized experiment: the Hansen and Bowers omnibus test across 81 covariates
reports a $p$-value of `r xb0i$overall[,"p.value"]`. That is, it would be
surprising to see the overall differences that we do see here, if, in fact, the
study were a randomized experiment.


```{r}
## Another way to see the same result
initial_neigh_bal_fmla <- ~soldvsnot17
tmpfmla <- formula(terms(parms1_res$maxTp@statistic@y))
lhs(initial_neigh_bal_fmla) <- rhs(tmpfmla)
initial_omnibus_bal <-
    independence_test(initial_neigh_bal_fmla,data=dat17p,teststat="quadratic")
pvalue(initial_omnibus_bal)
## Despite many covariates, the distribution looks good here.
initial_omnibus_bal_perm <-
    independence_test(initial_neigh_bal_fmla,data=dat17p,teststat="quadratic",distribution=approximate(nresample=10000))
pvalue(initial_omnibus_bal_perm)
```

## Designing a Better Baseline Comparison

Our strategy to finding comparisons between people living near selling versus
non-selling pharmacies involves stratification: we will be creating pairs of
people, one of whom lives near a selling pharmacy and one of whom lives in a
non-selling pharmacy, where the two people are similiar in baseline
characteristics and the two neighborhoods and pharmacies are also similar.

Why create pairs? Let's consider the hypothetical case of a pair-randomized
experiment. If we had managed to convince the government to issue the
registrations by lottery and if a large pool of pharmacies had entered the
lottery, we would be able to say that the pharmacies and nearby neighborhoods
selected by lottery to sell cannabis would be no different from the pharmacies
and associated neighborhoods losing the lottery. This would also be the case if
the lottery occurred in groups of places --- say, the right to sell were
randomly assigned among pharmacies in Montevideo and also among pharmacies
outside of Montevideo.  This kind of design would yield a block-randomized
experiment. If Montevideo/Interior were the only observed covariates that might
confound our comparison, we could directly compare pharmacies to each other
within area, and we could compare that stratified design to a hypothetical
block-randomized experiment in order to assess the comparison (just as we did
above when we compared the simple selling-vs-not selling comparison to a simple
randomized experiment with 16 treated and 42 control groups and 81 background
covariates).  This is what we do below. We use an optimization strategy to
produce a series of strata that collectively, across observed covariates,
compares favorably to a hypothetical block-randomized experiment. Of course, we
do not claim that a stratified design substitutes for an experiment --- we can
only speak to differences on the covariates we observed, not on all possible
observed and unobserved as we could if we had an actually randomized experiment.
Later, in \S~\ref{sec:sensitivity}, we assess the extent to which we might
change our substantive conclusions based on the stratified design due to the
influence of unobserved covariates.\footnote{See [@rosenbaum2010design], Chapter 3 for an overview of this method of sensitivity analysis.}

Our specific design first creates strata with similar neighborhoods where one
neighborhood has a pharmarcy selling marijuana and the other comparison
neighborhoods were places where a pharmacy did not sell marijuana. This design
compared favorably with a randomized experiment. The algorithm ended up dropping
13 neighborhoods as too different from the focal neighborhoods.

For example, it created 14 pairs and two sets with one selling pharmacy and two
non-selling pharmacies. It also dropped 24 comparison pharmacies. The comparison
to a randomized experiment across many covariates suggests little evidence
against the idea that this design is compatible with the randomized hypothetical
design.
```{r}
summary(parms1_res$fm_p,max.controls=Inf)
pvalue(parms1_res$maxTp)
```

To further return differences in exposure to a selling pharmacy, we next matched
people to each other within the sets just described: we required pairs, so we
end up with 160 pairs of people. Within each pair, we have one person living in
a neighborhood where a pharmacy sold marijuana and one person living in a
previously matched neighborhood where a pharmacy did not sell marijuana.
Although we know that we have made good pharmacy-level comparisons, we further
evaluate this individual level design using just the key outcomes as measured at
baseline (number of violent robberies in the neighborhood, robberies in the
neighborhood, and perceptions of neighborhood safety by people). We see that
these pairs of people differ little from what would be expected in a randomized
experiment in which exposure to a pharmacy selling marijuana  was randomly
assigned to people within pair. These pairs of people were all within the
pharmacy level sets, so that a comparison with a pair of people is also a
comparison between two pharmacies that were matched as above.

```{r}
summary(parms1_res$fm_i,max.controls=Inf)
parms1_res$crime_p
```

# Analysis Plan

## Outcomes

We also have a social disorder index: `social_dis` made from  "dis4_i" "dis5_i" "dis6_i" Higher values of the index indicates higher disorder.

Finally, we have created the "activities_index" that show how much people are involved in their neighborhood´s daily life.  This index has a 0-1 scale, 1 meaning greater frequency of activities in the neighborhood and 0 meaning none.  "neigh2_i" "neigh3_i" "neigh4_i" "neigh5_i" "neigh6_i" "neigh7_i" "neigh8_i".

Our outcome variables are the following:

```{r}
outcomes <- c("n_sec_i","c_sec_i","vic12","dt_impact_i","ps_impact_i","boca1_i","social_dis","activities_index")
```




| Hypothesis | Outcome | Variable(s) |
|------------ | -------- | ---------------|
| H1 | Neighbors' crime victimization in the last 12 months  |  vic12 |
| H2 |Neighbors' insecurity perceptions. Country and neighborhood | c_sec_i and n_sec_i |
| H3 | Existence of "bocas" in the neighborhood  | boca1_i |
| H4 | Social Disorder Index  | social_dis |
| H5 | Neighbors' insertion in neighborhood  | activities_index  |
| H6 | Law's perceived of impact on public security  | ps_impact_i  |
| H7 | Law's perceived of impact on drug trafficking | dt_impact_i  |

# Hypotheses

We developed and motivated these hypotheses in our literature review and
synthesis, not shown here. We list them here as a guide to our analysis.

Our  two main confirmatory hypotheses are:
  -   H1: *Crime victimization of pharmacies' neighbors will not differ between
    people living near selling versus non-selling pharmacies*

  -   H2: *Neighbors' insecurity perceptions  will not differ between
    people living near selling versus non-selling pharmacies*

 In adittion we have five exploratory hypotheses:

  -   H3: *The sale of marijuana at pharmacies will push "bocas" outside the
      neighborhood, and by doing that, neighbors' insecurity perception
      might be reduced*

  -   H4: *The sale of marijuana at pharmacies will increase social disorder
      in the neighborhood, that would lead to higher levels of public
      insecurity perception among neighbors*

  -   H5: *The sale of marijuana at pharmacies will diminish citizens'
      overall connection with and participation in the neighborhood*

  -   H6: *The sale of marijuana at pharmacies will not change citizens'
      evaluations about the impact of marijuana legalization on public
      security*

  -   H7: *The sale of marijuana at pharmacies will change citizens'
      evaluations about the impact of marijuana legalization on drug
      trafficking*

# Measures and Index Construction

The social disorder index was built using three variables measured using the
surveys:  perceptions of presence of young people loitering, perceptions of
presence of drunk or stoned people in the streets, and perceptions of presence
of people arguing with each other. Each of these variables have the following
values: 1 (Not at all), 2 (Little), 3 (Somewhat), and 4 (Very much).  In order
to construct the index we assume intermediate substitutability among variables
and assign the mean value \cite{goertz2006social}.

Citizens' Connection to their Neighborhood is an index constructed with eight
variables grouped in four dimensions. The dimensions are: use of services
(education and health) in the neighborhood, contact among neighbors (chat and/or
meet for collective action activities), perform recreational activities in the
neighborhood, and shopping in the neighborhood. We assume intermediate
substitutability among dimensions and assign the mean value. The use of services
dimension has two indicators: use of educational services (kindergarten,
school,high school) in the neighborhood and use of health services (doctor,
hospital) in the neighborhood. We assume total substitutability among the two
indicators and assign the maximum value  \cite{goertz2006social}.Contact among
neighbors dimension also has two indicators: talk with your neighbors and meets/
organizes with the neighbors for any improvement activity for the neighborhood.
We also assume total substitutability among the two indicators and assign the
maximum value. Perform recreational activities in the neighborhood is measured
by the question: do you perform any recreational activities in the neighborhood?
Finally, shopping in the neighborhood is measured by the question: do you
purchase in warehouses or stores in the neighborhood?

We document our index construction in the github repository in `datasetup.do`.

Table 1. Outcomes variables description

Variable	|	Question	|	Scale	|	Minimum	|	Maximun|
--------	|	--------	|	-----	|	:--------:|	:-------:|
Country insecurity perception | In general, in your country, do you feel very safe somewhat unsafe or very unsafe? |1. Very safe; 2.Somewhat safe; 3. Somewhat unsafe; 4. Very unsafe; 88 - Don\'t know; 99 - No answer |	1	|	4
Neighborhood insecurity perception | And in the neighborhood where you live, do you feel very safe, somewhat safe, somewhat unsafe or very unsafe? |1. Very safe; 2.Somewhat safe; 3. Somewhat unsafe; 4. Very unsafe; 88 - Don\'t know; 99 - No answer |	1	|	4
Crime victimization in the last 12 months | Now, changing the subject, have you been a victim of any type of crime in the past 12 months? That is, have you been a victim of robbery, burglary, assault, fraud, blackmail, extortion, violent threats or any other type of crime in the past 12 months? | 1. Yes; 2. No; 88 - Don\'t know | 1	|	2
Perceived impact on public security |	Now regarding to public safety, because of this law, do you think the country will be better, will remain the same or will be worst?	|	1. Yes;	2. No; 88 - Don\'t know;	99 - No answer| 1	|	3
Perceived impact on drug-trafficking | And regarging the fight against drug-trafficking, do you think the country will be better, will remain the same or will be worst? |	1. Yes;	2. No; 88 - Don\'t know;	99 - No answer| 1	|	2
Reported existence of bocas	|	Based on what you know or hear, there is a any boca in this area? | 1. Yes;	2. No; 88 - Don\'t know;	99 - No answer| 1	|	2
Social Disorder Index	|	Index | 1. Nothing; 2. A little; 3. Something; 4. A lot | 4 | 1
Presence of young people loitering | Observation | 1. Nothing; 2. A little; 3. Something; 4. A lot | 4 | 1
Presence of drunk or stoned people in the streets | Observation | 1. Nothing; 2. A little; 3. Something; 4. A lot | 4 | 1
Presence of people arguing with each other | Observation | 1. Nothing; 2. A little; 3. Something; 4. A lot | 1 | 4
Citizens insertion in the neighborhood | Index | - | 0 | 1
Talk with your neighbors| Finally, thinking about the activities you do in this neighborhood, please tell me how many times you: talk with your neighbors |1. Once a week; 2. Once or twice a week; 3. Once or twice a year; 4. Never; 88. Don\'t know; 99. No answer; |4 | 1
Chat and/or meet for collective action activities | Finally, thinking about the activities you do in this neighborhood, please tell me how many times you: chat and/or meet for collective action activities|1. Once a week; 2. Once or twice a week; 3. Once or twice a year; 4. Never; 88. Don\'t know; 99. No answer; | 4 | 1
Use educational services (kindergarten, school, high school) | Finally, thinking about the activities you do in this neighborhood, please tell me how many times you: use educational services (kindergarten, school, high school)|1. Once a week; 2. Once or twice a week; 3. Once or twice a year; 4. Never; 88. Don\'t know; 99. No answer; | 4 | 1
Use health services (doctor, hospital) | Finally, thinking about the activities you do in this neighborhood, please tell me how many times you: use health services (doctor, hospital) |1. Once a week; 2. Once or twice a week; 3. Once or twice a year; 4. Never; 88. Don\'t know; 99. No answer; | 4 | 1
Buy in local stores | Finally, thinking about the activities you do in this neighborhood, please tell me how many times you: buy in local stores|1. Once a week; 2. Once or twice a week; 3. Once or twice a year; 4. Never; 88. Don\'t know; 99. No answer; | 4 | 1
Perform recreational activities | Finally, thinking about the activities you do in this neighborhood, please tell me how many times you: perform recreational activities|1. Once a week; 2. Once or twice a week; 3. Once or twice a year; 4. Never; 88. Don\'t know; 99. No answer; | 4 | 1


# Estimation Procedure and Inference Criteria

We will estimate the average effect of living near a pharmacy that sells
marijuana using differences of means conditional on matched set, adjusting the
standard errors for hypothesis testing and confidence interval creation using
the CR2 cluster-robust standard errors at the level of the neighborhood (cite). All of this will occur using the
`lm_robust()` command from the `estimatr` package in R. For example, if
`soldvsnot17` is an indicator of whether a pharmacy sold marijuana and `fm_i` is
an indicator of pair and `Q56` is a neighborhood indicator, then we will
estimate effects and calculate confidence intervals for the average effect as
follows:

```{r eval=FALSE}
lm1 <- lm_robust(outcome1~soldvsnot17,fixed_effects=~fm_i,cluster=Q56,data=dat17i)
```

## Subgroup analysis

We expect that the effects of living near a pharmacy should be weaker for those
people living near the ``dropout'' pharmacies if living near a pharmacy does
matter for the outcomes. We also assess this exploratory hypothesis using the
same analytic strategy as above, but allowing different effects for people
living near the dropout pharmacies. For example, we would use code like this:

```{r eval=FALSE}
lm2 <- lm_robust(outcome1~soldvsnot17*I(dropout),fixed_effects=~fm_i,cluster=Q56,data=dat17i)
```

## Approach to multiple testing

We have 8 outcomes and one comparison (Selling versus Not Selling pharmacy). If
we were going to make a decision about the effect of the pharmacies if *any one
of the 8 comparisons yielded a p<.05*  then  we would make a false positive
error not 1 in 20 tests, but $1 − (1 − .05)^8 \approx 1/3$  or almost 7/20.

However,  if each analysis stands alone in terms of our  decision making: the
assessment of perceptions of insecurity can be null  or significant
independently of the assessment of reports of experiences with crime, then we
do not need to adjust the tests.

In the case of this project, we do not make any adjustment because decisions
regarding the effect of the pharmacy stand alone.

# Missing  Data  and Extreme Data Points

Since our data are from a survey we do not anticipate extreme data points in the endline --- our  work with the baseline  data supports this idea that we should not worry about overly influential points


### Sensitivity Analysis

We will conduct a sensitivity analysis using both the Rosenbaum style approach
(probably using the `senstrat` package for R) and the Cinelli and Hazlett
approach (using the `sensmakr` package for R).



# References
